On hyperparameter tuning through Lipschitz global optimization

### 2023-09-01 2023/ITMO paper/elsarticle-template-num.tex
minor fix

The simplest way to find the global optimum is the exhaustive search method (search on the uniform \cite{Bao2006} or random \cite{Bergstra2012} grid). 
By selecting the number of analyzed variants for each of the hyperparameters, searching all the resulting combinations and choosing the best of them in a given metric, we obtain an estimate of the optimum with a certain accuracy \cite{Nevendra2022}. The exhaustive search method is easy to implement, it has perfect parallelism, but it has a significant drawback (an exponential growth of the number of grid nodes as the number of hyperparameters increases). Thus, exhaustive search can be used as a method for solving HPO problems only in "simple" problems where both the number of hyperparameters (one or two) and the time for solving the initial problem with each selected combination of hyperparameters are small.

@@

Of particular interest are problems where some of the parameters can assume values from a predetermined finite set, since it is more difficult to construct estimates of the optimum for these problems than for problems with continuous parameters. Many publications address the methods for solving mixed-parameter problems (see, for example, reviews \cite{Burer2012,Boukouvala2016}). Known deterministic methods for solving problems of this class are centered on solving linear or convex problems \cite{Lee2012}. It is suggested that complex multi-extremal problems should be solved using heuristic approaches \cite{Belotti2013}.

@@

\section*{Code availability}
%проверить перевод
Software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.

\section*{Acknowledgements}
%уточнить ссылку
This research was supported by the research center ``Strong Artificial Intelligence in Industry'' of ITMO University.

>>>>

The simplest way to find the global optimum is the exhaustive search method (search on a uniform \cite{Bao2006} or random \cite{Bergstra2012} grid). 
By selecting the number of analyzed variants for each of the hyperparameters, searching all the resulting combinations and choosing the best of them in a given metric, we obtain an estimate of the optimum with a certain accuracy \cite{Nevendra2022}. The exhaustive search method is easy to implement, it has perfect parallelism, but it has a significant drawback (an exponential growth of the number of grid nodes as the number of hyperparameters increases). Thus, exhaustive search can be used as a method for solving HPO problems only in ``simple'' problems where both the number of hyperparameters (one or two) and the time for solving the initial problem with each selected combination of hyperparameters are small.

@@

Of particular interest are problems where some of the parameters can assume values from a predetermined finite set, since it is more difficult to construct estimates of the optimum for these problems than for problems with continuous parameters. Many publications address the methods for solving mixed-parameter problems (see, for example, reviews \cite{Burer2012,Boukouvala2016}). Known deterministic methods for solving problems of this class are centered on solving linear or convex problems \cite{Lee2012}. It is suggested that complex multiextremal problems should be solved using heuristic approaches \cite{Belotti2013}.

@@

\section*{Code availability}
The software that implements all of the described methods is available in the open repository \url{https://github.com/aimclub/iOpt/}.

\section*{Acknowledgements}
This work was supported by the Analytical Center for the Government of the Russian Federation (IGK 000000D730321P5Q0002), agreement No. 70-2021-00141.
